Preserving Reciprocal Consistency in Distributed Graph Databases

### 2020-04-07 paper/commands.tex
rename tikz node
section 2

% tikz
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
\tikzstyle{vertex2} = [circle, minimum width=40pt,draw,inner sep=0pt]
\tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
\tikzstyle{local} = [thick,->,>=stealth]
\tikzstyle{dist} = [thick,dashed,->,>=stealth]
\tikzstyle{node}=[circle,draw,radius=0.3, align=center]

@@

>>>>

    % tikz
    \usetikzlibrary{decorations.pathmorphing}
    \tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
    \tikzstyle{big_vertex} = [circle, minimum width=40pt,draw,inner sep=0pt]
    \tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
    \tikzstyle{local} = [thick,->,>=stealth]
    \tikzstyle{dist} = [thick,dashed,->,>=stealth]
    \tikzstyle{node}=[circle,draw,radius=0.3, align=center]

@@

            \def\record(#1,#2,#3,#4,#5,#6){
              \node (v) [draw,black,minimum height=0.7cm,minimum width=1cm,text width=0.2\linewidth,xshift=-6cm,align=center,yshift=#1cm] {#2};

            \node (b) [draw,black,minimum height=0.7cm,minimum width=11.4cm,text width=0.2\linewidth,xshift=1.4cm,yshift=#1cm] {};

            \draw[thick,->] (v) -- (b);

            \node (i1)  [draw,black,minimum height=0.5cm,minimum width=2cm,xshift=-2.8cm,text width=0.3\linewidth,yshift=#1cm,align=center] {#3};

            \node (i2)  [draw,black,minimum height=0.5cm,minimum width=2.5cm,xshift=0.9cm,right of=i1,yshift=0cm,text width=0.3\linewidth,align=center] {#4};

            \node (i3)  [draw,black,minimum height=0.5cm,minimum width=2.5cm,xshift=0.75cm,right of=i2,yshift=0cm,align=center] {#5};

            \node (i4)  [draw,black,minimum height=0.5cm,minimum width=2.5cm,xshift=0.6cm,right of=i3,yshift=0cm,align=center] {#6};

        }

\def\spaceRecord(#1){
\node (v) [black,minimum height=0.7cm,minimum width=1cm,text width=0.2\linewidth,xshift=-6cm,align=center,yshift=#1cm] {$\vdots$};
\node (b) [black,minimum height=0.7cm,minimum width=11.4cm,text width=0.2\linewidth,xshift=1.4cm,yshift=#1cm] {};
\node (i1)  [black,minimum height=0.5cm,minimum width=2cm,xshift=-2.8cm,text width=0.3\linewidth,yshift=#1cm,align=center] {$\vdots$};
\node (i2)  [black,minimum height=0.5cm,minimum width=2.5cm,xshift=0.9cm,right of=i1,yshift=0cm,text width=0.3\linewidth,align=center] {$\vdots$};
\node (i3)  [minimum height=0.5cm,minimum width=2.5cm,xshift=0.75cm,right of=i2,yshift=0cm,align=center] {$\vdots$};
\node (i4)  [minimum height=0.5cm,minimum width=2.5cm,xshift=0.6cm,right of=i3,yshift=0cm,align=center] {$\vdots$};
}

### 2020-04-07 paper/corruption.tex
section 2

>>>>

This section must be re-structured for ease of understanding.
First talk about transactions interleaving - narrative using fig 4.
Explain: Interleavings lead to half-corruption.
Exemplify half corruption using the first half of the code example.
Relate to dirty write..
Explain how half-corruption then leads to  sematic corruption and operational corruption.
Exemplify it using the second half of the coded example - unknown author.
Finally relate half corruption to Read Uncommitted.

\input{figures/hc}
